Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-19 manuscript/manuscript.tex
added changes

Brandes\cite{brandes} gives an exact algorithm for computing betweenness centrality of all the nodes that is based on solving a single-source shortest path (SSSP) problem for each node. A SSSP computation from $s$ produces a directed acyclic graph (DAG) encoding all shortest paths starting at $s$. The contributions of these paths to the betweenness counters can be computed in linear time using backward aggregation. Brandes' algorithm calculates $\sigma_{st}$  simultaneously with the shortest path calculations: $\sigma_{ss} = 1$ and for $s \neq t, \sigma_{st} = \sum_{v \in pred(t)} \sigma_{sv}$ where $pred(t)$ is a collection of the immediate predecessors of  $t$ on every shortes path ending at $t$. In a subsequent aggregation phase, nodes are processed by non-decreasing distance from $s$. So we have: 
$$\delta_{s}(v) = \sum_{w \in succ(v)} \frac{\sigma_{sv}}{\sigma_{sw}}(1+\delta_{s}(w))$$

>>>>

Brandes\cite{brandes} proposed an exact algorithm for computing betweenness centrality of all the nodes based on single source shortest path approach. A SSSP computation from $s$ yields a directed acyclic graph (DAG) representing all shortest paths starting at $s$. The contributions of these paths to the betweenness counters is computed in linear time using backward aggregation. Brandes' algorithm calculates $\sigma_{st}$  simultaneously with the shortest path calculations: $\sigma_{ss} = 1$ and for $s \neq t, \sigma_{st} = \sum_{v \in pred(t)} \sigma_{sv}$ where $pred(t)$ is a set of the immediate predecessors of  $t$ on every shortest path ending at $t$. In a subsequent aggregation phase, nodes are processed by non-decreasing distance from $s$. So we have: 
$$\delta_{s}(v) = \sum_{w \in succ(v)} \frac{\sigma_{sv}}{\sigma_{sw}}(1+\delta_{s}(w))$$
